---
title: "case study"
output: github_document
---

The thing we start all files with:

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.clour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

sclae_colour_discrete = scale_color_viridis_d()
scale_fill_discrete = scale_fill_viridis_d
```


## Load a dataset

```{r}
data("nyc_airbnb")

#View data
str(nyc_airbnb)

nyc_airbnb %>%
  count(room_type)

nyc_airbnb %>%
  count(neighbourhood_group)
```

* How many rentals are there? what type? Where?
* Is price correlated with review score?
* Which neighborhood is most popular? Most expensive?
* Which neighborhood has highest reviews?
* Is availability related to price?
* Is room type related to neighborhood?
* Is length of stay related to neighborhood group (borough)?

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location/2) %>% 
  rename (borough = neighbourhood_group)
```

Let's count things:

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)
  
```

We get the same table and it may be easier to get other info if we do it this way:

```{r, eval=FALSE}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```


Let's look at price and room type ...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighbourhood

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 

arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan", price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() +
  facet_grid(. ~ room_type)
```

Look at that coord flip!


Price vs location

_using `sample_n` because it's a huge dataset_

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.5)
```






